Competence distance

### 2017-03-01 analysis/analysis_competence.Rmd
update computation of index

# Read data 
```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# density data 
compete <- read.csv(file=paste0(di, '/data/tree_compete.csv'), header=TRUE, sep=',')
```

```{r}
radius_plot <- 10 #
sf_plot <- pi * radius_plot^2

den_tree <- compete %>% 
  group_by(id_core) %>% 
  summarise(abun = n(), 
            den = abun*10000 / sf_plot ) # stand density (tree / ha)

>>>>

# Read data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# density data 
compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')
```

```{r}
# Compute diameter normal (in meters)
compete <- compete %>% 
  mutate(dn = (perim_mm/1000) /pi) 
```

```{r}
focal_trees <- unique(compete$id_core)

output<- vector("list", length(focal_trees))

for (i in 1:length(focal_trees)){

# Create df   
df <- compete %>% 
  filter(id_core == focal_trees[[i]])

# Fixed Variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)
dnft <- filter(df, sp== 'Focal')$dn # normal diameter focal tree    
# ----------

# Competence indices 
## Number of competitors (r = 10)
n_competitors <- filter(df, sp != 'Focal') %>% count()

## Number of competitors with dn_j > dn_i (focal tree)
n_competitors_hihger <- df %>%
  filter(sp != 'Focal') %>%
  filter(dn > dnft) %>% 
  count()

## Plot density (tree/plot)
plot_density <- n_competitors / sf_plot

## Stand density (tree / ha) 
stand_density <- (n_competitors * 10000) / sf_plot

## Sum sizes 
sum_sizes <- df %>% 
  filter(sp != 'Focal') %>%
  summarise(sum_sizes=sum(dn))

## Size ratio 
size_ratio <- dnft / (dnft + sum_sizes$sum_sizes)

## Distance nearest tree
dist_nn <- df %>% 
  filter(sp != 'Focal') %>% 
  slice(which.min(distance_cm))

dist_nn <- (dist_nn$distance_cm / 100)

## Various 
### Basal area
### Size ratio proportional to distance 
### Size difference proportional to distance 
### Negative exponential size ratio
### Negative exponential weighted size ratio
### Lorimer 
### Crowding 
df_more_indices <- df %>%
  filter(sp != 'Focal') %>%
  mutate(
    basal_area = ((pi/4) * dn * dn), 
    size_ratio_distance = (dn / dnft) * (1 / ((distance_cm/100) + 1)),
    size_diff_distance = (dn - dnft) / ((distance_cm/100) + 1),
    neg_exp_size_ratio = (dn / dnft) * (1 / exp((distance_cm/100) + 1)),
    neg_exp_w_size_ratio = (dn / dnft) * exp((-(distance_cm/100) + 1) / (dn + dnft)),
    lorimer = (dn / dnft) / (sqrt((distance_cm/100) / radius_plot)),
    crowding = dn / (distance_cm/100))

df_indices <- df_more_indices %>% 
  summarise(ba = sum(basal_area),
            srd = sum(size_ratio_distance),
            sdd = sum(size_diff_distance),
            nesr = sum(neg_exp_size_ratio),
            newsr = sum(neg_exp_w_size_ratio),
            lorimer = sum(lorimer),
            crowding = sum(crowding)) %>% 
  mutate(nc = n_competitors,
         nch = n_competitors_hihger,
         pd = plot_density,
         std = stand_density,
         ss = sum_sizes,
         sr = size_ratio,
         dnn = dist_nn, 
         id_plot = focal_trees[[i]])

output[[i]] <- df_indices 
}

df_indices_plot <- bind_rows(output)
```

```{r}
# Some constante variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)

den_tree <- compete %>% 
  filter(sp != 'Focal') %>% 
  group_by(id_core) %>% 
  summarise(ntree = n(), 
            stand_density = ntree*10000 / sf_plot ) # stand density (tree / ha)
